---
title: "Twitter Summary"
author: "Armenoush Aslanian-Persico"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: true
    code_folding: show
    theme: spacelab
---
# Libraries

```{r, eval=FALSE}
library('knitr')
library('markdown')
library('tidyr')
library('RCurl')
library('plyr')
library('dplyr')
library('ggplot2')
```

```{r, eval=TRUE, include=FALSE}
library('knitr')
library('markdown')
library('tidyr')
library('RCurl')
library('plyr')
library('dplyr')
library('ggplot2')
```


# Sources

https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.03.2016.csv

https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.04.2016.csv

https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.05.2016.csv

https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.06.2016.csv

https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.07.2016.csv

https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.08.2016.csv





# 2016-05-03

## Import CSV
```{r}

x503 <- getURL("https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.03.2016.csv") #import twitter CSV

tweets503<- data.frame(read.csv(text=x503, header=T)) #create data frame

kable(head(tweets503,3)) #show head
dim(tweets503)
```

## Movie Score

```{r}
moviesum503<- ddply(tweets503, .(movie), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by movie
      
kable(moviesum503)
```

## Movie and City Score

```{r, eval=FALSE}
moviecitysum503<- ddply(tweets503, .(movie, city), summarize,  Sentiment_Score=mean(Sentiment_Score)) #summarize by movie and city
      
kable(moviecitysum503)
```

## City Score

```{r}
citysum503<- ddply(tweets503, .(city), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by city
      
kable(citysum503)
```

## Unique Movies
```{r}
allmovies503<-unique(tweets503[c("movie")]) # get unique movies
allmovies503$num<-seq.int(nrow(allmovies503)) # add counter row
kable(allmovies503) #show unique values for movie name

```

## Graphs
```{r}
ggplot(
  moviesum503, aes(x = reorder(movie,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("Movie Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="Movies",y="Score")

ggplot(
  citysum503, aes(x = reorder(city,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("City Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="City",y="Score")

```



# 2016-05-04

## Import CSV
```{r}

x504 <- getURL("https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.04.2016.csv") #import twitter CSV

tweets504<- data.frame(read.csv(text=x504, header=T)) #create data frame

kable(head(tweets504,3)) #show head
#dim(tweets504)
```

## Movie Score

```{r}
moviesum504<- ddply(tweets504, .(movie), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by movie
kable(moviesum504)
```

## Movie and City Score

```{r, eval=FALSE}
moviecitysum504<- ddply(tweets504, .(movie, city), summarize,  Sentiment_Score=mean(Sentiment_Score)) #summarize by movie and city
kable(moviecitysum504)
```

## City Score

```{r}
citysum504<- ddply(tweets504, .(city), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by city
kable(citysum504)
```

## Unique Movies

```{r}
allmovies504<-unique(tweets504[c("movie")]) # get unique movies
allmovies504$num<-seq.int(nrow(allmovies504)) # add counter row
kable(allmovies504) #show unique values for movie name
```

## Graphs

```{r}
ggplot(
  moviesum504, aes(x = reorder(movie,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("Movie Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="Movies",y="Score")

ggplot(
  citysum504, aes(x = reorder(city,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("City Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="City",y="Score")
```


# 2016-05-05

## Import CSV
```{r}

x505 <- getURL("https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.05.2016.csv") #import twitter CSV

tweets505<- data.frame(read.csv(text=x505, header=T)) #create data frame

kable(head(tweets505,3)) #show head
#dim(tweets505)
```

## Movie Score

```{r}
moviesum505<- ddply(tweets505, .(movie), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by movie
kable(moviesum505)
```

## Movie and City Score

```{r, eval=FALSE}
moviecitysum505<- ddply(tweets505, .(movie, city), summarize,  Sentiment_Score=mean(Sentiment_Score)) #summarize by movie and city
kable(moviecitysum505)
```

## City Score

```{r}
citysum505<- ddply(tweets505, .(city), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by city
kable(citysum505)
```

## Unique Movies
```{r}
allmovies505<-unique(tweets505[c("movie")]) # get unique movies
allmovies505$num<-seq.int(nrow(allmovies505)) # add counter row
kable(allmovies505) #show unique values for movie name
```

## Graphs
```{r}
ggplot(
  moviesum505, aes(x = reorder(movie,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("Movie Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="Movies",y="Score")

ggplot(
  citysum505, aes(x = reorder(city,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("City Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="City",y="Score")
```


# 2016-05-06

## Import CSV
```{r}
x506 <- getURL("https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.06.2016.csv") #import twitter CSV
tweets506<- data.frame(read.csv(text=x506, header=T)) #create data frame
kable(head(tweets506,3)) #show head
#dim(tweets506)
```

## Movie Score

```{r}
moviesum506<- ddply(tweets506, .(movie), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by movie
kable(moviesum506)
```

## Movie and City Score

```{r, eval=FALSE}
moviecitysum506<- ddply(tweets506, .(movie, city), summarize,  Sentiment_Score=mean(Sentiment_Score)) #summarize by movie and city
kable(moviecitysum506)
```

## City Score

```{r}
citysum506<- ddply(tweets506, .(city), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by city
kable(citysum506)
```

## Unique Movies
```{r}
allmovies506<-unique(tweets506[c("movie")]) # get unique movies
allmovies506$num<-seq.int(nrow(allmovies506)) # add counter row
kable(allmovies506) #show unique values for movie name
```

## Graphs
```{r}
ggplot(
  moviesum506, aes(x = reorder(movie,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("Movie Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="Movies",y="Score")

ggplot(
  citysum506, aes(x = reorder(city,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("City Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="City",y="Score")
```


# 2016-05-07

## Import CSV
```{r}
x507 <- getURL("https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.07.2016.csv") #import twitter CSV
tweets507<- data.frame(read.csv(text=x507, header=T)) #create data frame
kable(head(tweets507,3)) #show head
#dim(tweets507)
```

## Movie Score

```{r}
moviesum507<- ddply(tweets507, .(movie), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by movie
kable(moviesum507)
```

## Movie and City Score

```{r, eval=FALSE}
moviecitysum507<- ddply(tweets507, .(movie, city), summarize,  Sentiment_Score=mean(Sentiment_Score)) #summarize by movie and city
kable(moviecitysum507)
```

## City Score

```{r}
citysum507<- ddply(tweets507, .(city), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by city
kable(citysum507)
```

## Unique Movies

```{r}
allmovies507<-unique(tweets507[c("movie")]) # get unique movies
allmovies507$num<-seq.int(nrow(allmovies507)) # add counter row
kable(allmovies507) #show unique values for movie name
```

## Graphs

```{r}
ggplot(
  moviesum507, aes(x = reorder(movie,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("Movie Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="Movies",y="Score")

ggplot(
  citysum507, aes(x = reorder(city,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("City Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="City",y="Score")

```


# 2016-05-08

## Import CSV

```{r}

x508 <- getURL("https://raw.githubusercontent.com/spsstudent15/Data607FinalProject/master/Tweets%20for%2005.08.2016.csv") #import twitter CSV
tweets508<- data.frame(read.csv(text=x508, header=T)) #create data frame
kable(head(tweets508,3)) #show head
#dim(tweets508)
```

## Movie Score

```{r}
moviesum508<- ddply(tweets508, .(movie), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by movie
kable(moviesum508)
```

## Movie and City Score

```{r, eval=FALSE}
moviecitysum508<- ddply(tweets508, .(movie, city), summarize,  Sentiment_Score=mean(Sentiment_Score)) #summarize by movie and city
kable(moviecitysum508)
```

## City Score

```{r}
citysum508<- ddply(tweets508, .(city), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by city
kable(citysum508)
```

## Unique Movies

```{r}
allmovies508<-unique(tweets508[c("movie")]) # get unique movies
allmovies508$num<-seq.int(nrow(allmovies508)) # add counter row
kable(allmovies508) #show unique values for movie name

```

## Graphs

```{r}
ggplot(
  moviesum508, aes(x = reorder(movie,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("Movie Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="Movies",y="Score")

ggplot(
  citysum508, aes(x = reorder(city,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("City Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="City",y="Score")

```

# All Days Combined

```{r}
tweets1<- rbind(tweets503,tweets504,tweets505,tweets506,tweets507,tweets508)

#kable(head(tweets1))
#kable(tail(tweets1))
#dim(tweets1)
```

## Movie Score

```{r}
moviesum1<- ddply(tweets1, .(movie), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by movie
moviesum1$num<-seq.int(nrow(moviesum1)) # add counter row
kable(moviesum1)
```

## Movie and City Score

```{r, eval=FALSE}
moviecitysum1<- ddply(tweets1, .(movie, city), summarize,  Sentiment_Score=mean(Sentiment_Score)) #summarize by movie and city
kable(moviecitysum1)
```

## City Score

```{r}
citysum1<- ddply(tweets1, .(city), summarize,  Sentiment_Score=mean(Sentiment_Score), Count_of_Tweets=length(tweet)) #summarize by city
kable(citysum1)
```


```{r, include=FALSE}
# Not needed in summary section
allmovies1<-unique(tweets1[c("movie")]) # get unique movies
allmovies1$num<-seq.int(nrow(allmovies1)) # add counter row
kable(allmovies1) #show unique values for movie name

```

## Graphs
```{r}
ggplot(
  moviesum1, aes(x = reorder(movie,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("Movie Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="Movies",y="Score")

ggplot(
  citysum1, aes(x = reorder(city,Sentiment_Score), y = Sentiment_Score, fill=Sentiment_Score)) + 
  geom_bar(stat="identity") +
  ggtitle("City Average Sentiment Score")+ 
  theme(axis.text=element_text(angle=90))+
  labs(x="City",y="Score")
```


# Statistics

## Totals

```{r}
dim(tweets1)
dim(allmovies1)
```

## Tweet Count Per Day

```{r}
dim(tweets503)
dim(tweets504)
dim(tweets505)
dim(tweets506)
dim(tweets507)
dim(tweets508)
```

## Movie Count Per Day

```{r}
dim(allmovies503)
dim(allmovies504)
dim(allmovies505)
dim(allmovies506)
dim(allmovies507)
dim(allmovies508)

```